Current State of Knowledge Representation Systems for Robotics

### 2011-11-25 krs-survey.tex
Added paragraph on presupposition accomodation.
While here, moved the 'projection task' paragraph to the 'integration in robots' section

>>>>

\subsubsection{Knowledge acquisition and modalities merging}
\label{sect|knowledge-acquisition}

\emph{Presupposition accomodation} is the ability to acquire and represent
facts that are not grounded into perception. A typical example is a human
telling the robot that \emph{"big blue sphere is behind you!"}.

A knowledge representation system able to copte with presupposition
accomodation would be able to take into account this (usually under-defined)
information in later inference.

This ability to imagine a physically state of the world that is not actually
perceived can be seen as the converse of the grounding ability.

Note also that presupposition accomodation implies a bidirectional link of the
symbolic knowledge model with a geometric (or physical) model of the
environment. This article focuses on symbolic knowledge representation systems,
but we shall mention when a KRS explicitely provides support for presupposition
accomodation.

%%%%%
\subsection{Integration in robotic architectures}
\label{sect|integration-robot}
